Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
fixed some latex errors

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.7]{figures/arch.pdf}
  \end{center}
  \caption{The Data Processing Architecture}
  \label{fig:arch}
\end{figure}

@@

\begin{table}[t]
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{23em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistin a way that is particularly different from the other bugsakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.4]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
\end{figure*}

>>>>

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.9]{figures/arch.pdf}
  \end{center}
  \caption{The Data Processing Architecture}
  \label{fig:arch}
\end{figure}

@@

\begin{table}[t]
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{23em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
\end{figure*}
